---
title: "PQ GUI Tutorial"
author: "Wei Fu"
date: "Wednesday, May 06, 2015"
output: slidy_presentation
---

## Purpose

- It's designed to assist people in running model
    - User-friendly interface
    - Structured layout
    - Check/Warining system to ensure correct specification
- It's not designed for experiments on PERCH Quantitative Analysis.
    - less control over model setting (options for priors are )

## Reciept for PERCH pie

- REALLY REALLY understand PERCH
- Understand PERCH Quantitative Analysis
- Install softwares
- Install additional packages
- Download and run PQGUI app

## Install softwares

- WINBUGS
    - Please make sure it's installed in ***C:/Program Files/WinBUGS14/***
    - We are very close to successfully implement code in "Supercomputer" using *JAGS*

- R & R Studio

## Install additional packages
```{r, eval=FALSE}
install.packages("lubridate")
install.packages("devtools")
install.packages("sets")
install.packages("R2WinBUGS")
install.packages("gplots")
install.packages("RColorBrewer")
install.packages("binom")
install.packages("coda")
install.packages("ks")
install.packages("robCompositions")
install.packages(c("Rcpp", "httpuv", "shiny"))
devtools::install_github("zhenkewu/nplcm")
```
## Download and run PQGUI app

```{r, eval=FALSE}
shiny::runGitHub("PQGUI","fupangpangpang")
```




